---
title: "TGT"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, 
                      echo=TRUE, eval=TRUE)
```




## Functions for Estimating the Conditional VaR

```{r}
# function for estimating conditional quantile
kernel_con_q_est = function(X,Z,p,h){
    
    # generate grids for X & Z(quantile) directions
    xx = seq(min(X), max(X), length.out=1000)
    #xx = X[order(X)]
    qq = Z[order(Z)] 
    
    # calculate the weight Wi(x) for each x in the xx
    kernel_m = outer(xx,X,"-")
    kernel_d = dnorm(kernel_m/h)     # Gaussian Kernel with bandwidth h
    W = kernel_d / rowSums(kernel_d)
    
    # get the quantile q(x) for each x in the xx,  s.t. Fn(x) closest to p
    qq_est = rep(NA,length(xx))
    for (i in 1:length(xx)) {
        Fns = rep(NA,length(qq))
        for (j in 1:length(qq)) {
            Fns[j] = sum( W[i,]*(Z<=qq[j]) )  # element-wise production
        }
        index = which.min(abs(Fns-p))
        qq_est[i] = qq[index]
    }
    return(list(xx=xx, qq_est=qq_est))
}
```

```{r}
# estimate conditional quantile with "kernel conditional quantile estimation"
library(KernSmooth)

estimate_con_q = function(X,Z,p,h0.5=NULL,dpill_trim){
    # get h0.5 if not given
    if (is.null(h0.5)) { 
        h0.5 = dpill(X,Z, trim=dpill_trim,      #  trim = min(0.05,10/length(X))
                     blockmax=ceiling(length(X)/10), divisor=10)
    }
    
    # calculate optimal h
    opt_h = (2/pi * p*(1-p) * dnorm(qnorm(p))^(-2) * h0.5^5) ^ (1/5)
        
    # estimate conditional quantile using opt_h
    qq_est1 = kernel_con_q_est(X,Z,p,opt_h)
        
    # estimate conditional quantile using sqrt(2)*opt_h
    qq_est2 = kernel_con_q_est(X,Z,p,sqrt(2)*opt_h)
        
    # bias correction
    qq_est = 2*qq_est1$qq_est - qq_est2$qq_est
    
    return(list(xx=qq_est1$xx, qq_est=qq_est, h0.5=h0.5, opt_h=opt_h))
}
```


```{r}
# function for cutting off the extreme values
cut_data = function(X, Z, Date, cutoff=0.05){

    # cutoff the tail of each end
    cuts = as.vector(quantile(X, probs=c(cutoff,1-cutoff))) # both ends of X
    index = which((X>cuts[1]) & (X<cuts[2]))
    X_cut = X[index]
    Z_cut = Z[index]
    Date_cut = Date[index]

    return(list(X_cut=X_cut, Z_cut=Z_cut, Date_cut=Date_cut, cuts=cuts))
}
```






# Stock Daily Data

```{r}
data = read.csv('stock/TGT.csv')
data$Date = as.Date(data$Date)
c(min(data$Date), max(data$Date))
```

```{r}
# calculate the returns
data$return = rep(NA,nrow(data))
for (i in 2:nrow(data)) {
    data$return[i] = (data$Adj.Close[i] - data$Adj.Close[i-1])/data$Adj.Close[i-1]
}
data = data[-1,]
c(min(data$Date), max(data$Date))
```

```{r}
plot(return~Date,data, type="l", xlab="Date",ylab="return", main="Daily Return")
```




### (1) One Year - 2019

```{r}
sub_data = data[(data$Date>="2019-01-01")&(data$Date<="2019-12-31"), ]
c(min(sub_data$Date), max(sub_data$Date))
```

```{r}
Z = sub_data$return
n = length(Z)
X = Z[1:(n-1)]
Z = Z[2:n]
Date = sub_data$Date[2:n]
```

```{r}
plot(Date, Z, type="l", ylim=c(min(Z)-0.02,max(Z)+0.02),
     xlab="Date",ylab="return", main="Daily Return for 2019")

# check the distribution of return Zt
hist(Z, breaks=100, freq=FALSE, main="", xlab=expression(Z[t]))
lines(density(Z, adjust=1),col="red",lwd=2) # kernel density estimation
zz = seq(min(Z),max(Z),0.01)
lines(zz, dnorm(zz,mean(Z),sd(Z)), col="blue",lwd=2)

# check the scatterplot of {Xt, Zt} t=1,...,n
plot(X, Z, ylim=c(min(Z)-0.01,max(Z)+0.01), xlab=expression(X[t]), ylab=expression(Z[t]))
```



#### Cut the data

```{r}
cutted = cut_data(X, Z, Date, cutoff=0.05)
X_cut = cutted$X_cut
Z_cut = cutted$Z_cut
Date_cut = cutted$Date_cut
```

```{r}
plot(Date_cut, Z_cut, type="l", ylim=c(min(Z_cut)-0.02,max(Z_cut)+0.02),
     xlab="Date",ylab="return", main="Daily Return for 2019")

# check the distribution of return Zt
hist(Z_cut, breaks=100, freq=FALSE, main="", xlab=expression(Z[t]))
lines(density(Z_cut, adjust=1),col="red",lwd=2) # kernel density estimation
zz_cut = seq(min(Z_cut),max(Z_cut),0.01)
lines(zz_cut, dnorm(zz_cut,mean(Z_cut),sd(Z_cut)), col="blue",lwd=2)

# check the scatterplot of {Xt, Zt} t=1,...,n
plot(X_cut, Z_cut, ylim=c(min(Z_cut)-0.01,max(Z_cut)+0.01), xlab=expression(X[t]), ylab=expression(Z[t]))
```



#### Estimate the conditional quantile

```{r}
# estimate the conditional quantile (cutted)
est_01 = estimate_con_q(X_cut,Z_cut,p=1-0.99, dpill_trim=0.01)
est_05 = estimate_con_q(X_cut,Z_cut,p=1-0.95, dpill_trim=0.01)
c(est_01$h0.5, est_01$opt_h)
c(est_05$h0.5, est_05$opt_h)
```

```{r}
# plot estimated VaR on the scatterplot of {Xt, Zt} t=1,...,n  (cutted)
plot(X_cut, Z_cut, ylim=c(min(Z_cut)-0.03,max(Z_cut)+0.02), 
     xlab=expression(X[t]), ylab=expression(Z[t]), main="Daily Return for 1-Year (2019)")
lines(locpoly(est_01$xx,est_01$qq_est,kernel="normal",bandwidth=est_01$opt_h,gridsize=1000), col="blue")
lines(locpoly(est_05$xx,est_05$qq_est,kernel="normal",bandwidth=est_05$opt_h,gridsize=1000), col="red")
lines(locpoly(est_01$xx,est_01$qq_est,kernel="normal",bandwidth=est_01$opt_h,gridsize=1000,degree=2), col="green")
lines(locpoly(est_05$xx,est_05$qq_est,kernel="normal",bandwidth=est_05$opt_h,gridsize=1000,degree=2), col="orange")
legend("topleft",col=c("blue","red"),lty=1, cex=0.8,
       legend=c("Estimated 1% quantile (d=1)","Estimated 5% quantile (d=1)"))
legend("topright",col=c("green","orange"),lty=1, cex=0.8,
       legend=c("Estimated 1% quantile (d=2)","Estimated 5% quantile (d=2)"))
```







### (2) Two Year - 2018 & 2019

```{r}
sub_data = data[(data$Date>="2018-01-01")&(data$Date<="2019-12-31"), ]
c(min(sub_data$Date), max(sub_data$Date))
```

```{r}
Z = sub_data$return
n = length(Z)
X = Z[1:(n-1)]
Z = Z[2:n]
Date = sub_data$Date[2:n]
```

```{r}
plot(Date, Z, type="l", ylim=c(min(Z)-0.02,max(Z)+0.02),
     xlab="Date",ylab="return", main="Daily Return for 2018 - 2019")

# check the distribution of return Zt
hist(Z, breaks=100, freq=FALSE, main="", xlab=expression(Z[t]))
lines(density(Z, adjust=1),col="red",lwd=2) # kernel density estimation
zz = seq(min(Z),max(Z),0.01)
lines(zz, dnorm(zz,mean(Z),sd(Z)), col="blue",lwd=2)

# check the scatterplot of {Xt, Zt} t=1,...,n
plot(X, Z, ylim=c(min(Z)-0.01,max(Z)+0.01), xlab=expression(X[t]), ylab=expression(Z[t]))
```



#### Cut the data

```{r}
cutted = cut_data(X, Z, Date, cutoff=0.05)
X_cut = cutted$X_cut
Z_cut = cutted$Z_cut
Date_cut = cutted$Date_cut
```

```{r}
plot(Date_cut, Z_cut, type="l", ylim=c(min(Z_cut)-0.02,max(Z_cut)+0.02),
     xlab="Date",ylab="return", main="Daily Return for 2018 - 2019")

# check the distribution of return Zt
hist(Z_cut, breaks=100, freq=FALSE, main="", xlab=expression(Z[t]))
lines(density(Z_cut, adjust=1),col="red",lwd=2) # kernel density estimation
zz_cut = seq(min(Z_cut),max(Z_cut),0.01)
lines(zz_cut, dnorm(zz_cut,mean(Z_cut),sd(Z_cut)), col="blue",lwd=2)

# check the scatterplot of {Xt, Zt} t=1,...,n
plot(X_cut, Z_cut, ylim=c(min(Z_cut)-0.01,max(Z_cut)+0.01), xlab=expression(X[t]), ylab=expression(Z[t]))
```



#### Estimate the conditional quantile

```{r}
# estimate the conditional quantile (cutted)
est_01 = estimate_con_q(X_cut,Z_cut,p=1-0.99, dpill_trim=0.01)
est_05 = estimate_con_q(X_cut,Z_cut,p=1-0.95, dpill_trim=0.01)
c(est_01$h0.5, est_01$opt_h)
c(est_05$h0.5, est_05$opt_h)
```

```{r}
# plot estimated VaR on the scatterplot of {Xt, Zt} t=1,...,n  (cutted)
plot(X_cut, Z_cut, ylim=c(min(Z_cut)-0.03,max(Z_cut)+0.02), 
     xlab=expression(X[t]), ylab=expression(Z[t]), main="Daily Return for 2-Year (2018-2019)")
lines(locpoly(est_01$xx,est_01$qq_est,kernel="normal",bandwidth=est_01$opt_h,gridsize=1000), col="blue")
lines(locpoly(est_05$xx,est_05$qq_est,kernel="normal",bandwidth=est_05$opt_h,gridsize=1000), col="red")
lines(locpoly(est_01$xx,est_01$qq_est,kernel="normal",bandwidth=est_01$opt_h,gridsize=1000,degree=2), col="green")
lines(locpoly(est_05$xx,est_05$qq_est,kernel="normal",bandwidth=est_05$opt_h,gridsize=1000,degree=2), col="orange")
legend("topleft",col=c("blue","red"),lty=1, cex=0.8,
       legend=c("Estimated 1% quantile (d=1)","Estimated 5% quantile (d=1)"))
legend("topright",col=c("green","orange"),lty=1, cex=0.8,
       legend=c("Estimated 1% quantile (d=2)","Estimated 5% quantile (d=2)"))
```









### (3) Whole data - 2017-01-01 to 2020-05-01

```{r}
sub_data = data[(data$Date>="2017-01-01")&(data$Date<="2020-05-01"), ]
c(min(sub_data$Date), max(sub_data$Date))
```

```{r}
Z = sub_data$return
n = length(Z)
X = Z[1:(n-1)]
Z = Z[2:n]
Date = sub_data$Date[2:n]
```

```{r}
plot(Date, Z, type="l", ylim=c(min(Z)-0.02,max(Z)+0.02),
     xlab="Date",ylab="return", main="Daily Return")

# check the distribution of return Zt
hist(Z, breaks=100, freq=FALSE, main="", xlab=expression(Z[t]))
lines(density(Z, adjust=1),col="red",lwd=2) # kernel density estimation
zz = seq(min(Z),max(Z),0.01)
lines(zz, dnorm(zz,mean(Z),sd(Z)), col="blue",lwd=2)

# check the scatterplot of {Xt, Zt} t=1,...,n
plot(X, Z, ylim=c(min(Z)-0.01,max(Z)+0.01), xlab=expression(X[t]), ylab=expression(Z[t]))
```



#### Cut the data

```{r}
cutted = cut_data(X, Z, Date, cutoff=0.05)
X_cut = cutted$X_cut
Z_cut = cutted$Z_cut
Date_cut = cutted$Date_cut
```

```{r}
plot(Date_cut, Z_cut, type="l", ylim=c(min(Z_cut)-0.02,max(Z_cut)+0.02),
     xlab="Date",ylab="return", main="Daily Return")

# check the distribution of return Zt
hist(Z_cut, breaks=100, freq=FALSE, main="", xlab=expression(Z[t]))
lines(density(Z_cut, adjust=1),col="red",lwd=2) # kernel density estimation
zz_cut = seq(min(Z_cut),max(Z_cut),0.01)
lines(zz_cut, dnorm(zz_cut,mean(Z_cut),sd(Z_cut)), col="blue",lwd=2)

# check the scatterplot of {Xt, Zt} t=1,...,n
plot(X_cut, Z_cut, ylim=c(min(Z_cut)-0.01,max(Z_cut)+0.01), xlab=expression(X[t]), ylab=expression(Z[t]))
```



#### Estimate the conditional quantile

```{r}
# estimate the conditional quantile (cutted)
est_01 = estimate_con_q(X_cut,Z_cut,p=1-0.99, dpill_trim=0.01)
est_05 = estimate_con_q(X_cut,Z_cut,p=1-0.95, dpill_trim=0.01)
c(est_01$h0.5, est_01$opt_h)
c(est_05$h0.5, est_05$opt_h)
```

```{r}
# plot estimated VaR on the scatterplot of {Xt, Zt} t=1,...,n  (cutted)
plot(X_cut, Z_cut, ylim=c(min(Z_cut)-0.03,max(Z_cut)+0.02), 
     xlab=expression(X[t]), ylab=expression(Z[t]), main="Daily Return for over 3-Year (2017-now)")
lines(locpoly(est_01$xx,est_01$qq_est,kernel="normal",bandwidth=est_01$opt_h,gridsize=1000), col="blue")
lines(locpoly(est_05$xx,est_05$qq_est,kernel="normal",bandwidth=est_05$opt_h,gridsize=1000), col="red")
lines(locpoly(est_01$xx,est_01$qq_est,kernel="normal",bandwidth=est_01$opt_h,gridsize=1000,degree=2), col="green")
lines(locpoly(est_05$xx,est_05$qq_est,kernel="normal",bandwidth=est_05$opt_h,gridsize=1000,degree=2), col="orange")
legend("topleft",col=c("blue","red"),lty=1, cex=0.8,
       legend=c("Estimated 1% quantile (d=1)","Estimated 5% quantile (d=1)"))
legend("topright",col=c("green","orange"),lty=1, cex=0.8,
       legend=c("Estimated 1% quantile (d=2)","Estimated 5% quantile (d=2)"))
```










# Stock Monthly data

```{r}
mon_data = read.csv('stock/TGT_mon.csv')
mon_data$Date = as.Date(mon_data$Date)
c(min(mon_data$Date), max(mon_data$Date))
nrow(mon_data)
```

```{r}
# calculate the returns
mon_data$return = rep(NA,nrow(mon_data))
for (i in 2:nrow(mon_data)) {
    mon_data$return[i] = (mon_data$Adj.Close[i] - mon_data$Adj.Close[i-1])/mon_data$Adj.Close[i-1]
}
mon_data = mon_data[-1,]
c(min(mon_data$Date), max(mon_data$Date))
```

```{r}
plot(return~Date,mon_data, type="l", xlab="Month",ylab="return", main="Monthly Return")
```



### (1) Whole data

```{r}
sub_data = mon_data
c(min(sub_data$Date), max(sub_data$Date))
```

```{r}
Z = sub_data$return
n = length(Z)
X = Z[1:(n-1)]
Z = Z[2:n]
Date = sub_data$Date[2:n]
```

```{r}
plot(Date, Z, type="l", ylim=c(min(Z)-0.02,max(Z)+0.02),
     xlab="Month",ylab="return", main="Monthly Return")

# check the distribution of return Zt
hist(Z, breaks=100, freq=FALSE, main="", xlab=expression(Z[t]))
lines(density(Z, adjust=1),col="red",lwd=2) # kernel density estimation
zz = seq(min(Z),max(Z),0.01)
lines(zz, dnorm(zz,mean(Z),sd(Z)), col="blue",lwd=2)

# check the scatterplot of {Xt, Zt} t=1,...,n
plot(X, Z, ylim=c(min(Z)-0.02,max(Z)+0.02), xlab=expression(X[t]), ylab=expression(Z[t]))
```



#### Cut the data

```{r}
cutted = cut_data(X, Z, Date, cutoff=0.05)
X_cut = cutted$X_cut
Z_cut = cutted$Z_cut
Date_cut = cutted$Date_cut
```

```{r}
plot(Date_cut, Z_cut, type="l", ylim=c(min(Z_cut)-0.02,max(Z_cut)+0.02),
     xlab="Month",ylab="return", main="Monthly Return")

# check the distribution of return Zt
hist(Z_cut, breaks=100, freq=FALSE, main="", xlab=expression(Z[t]))
lines(density(Z_cut, adjust=1),col="red",lwd=2) # kernel density estimation
zz_cut = seq(min(Z_cut),max(Z_cut),0.01)
lines(zz_cut, dnorm(zz_cut,mean(Z_cut),sd(Z_cut)), col="blue",lwd=2)

# check the scatterplot of {Xt, Zt} t=1,...,n
plot(X_cut, Z_cut, ylim=c(min(Z_cut)-0.01,max(Z_cut)+0.01), xlab=expression(X[t]), ylab=expression(Z[t]))
```



#### Estimate the conditional quantile

```{r}
# estimate the conditional quantile (cutted)
est_01 = estimate_con_q(X_cut,Z_cut,p=1-0.99, dpill_trim=0.01)
est_05 = estimate_con_q(X_cut,Z_cut,p=1-0.95, dpill_trim=0.01)
c(est_01$h0.5, est_01$opt_h)
c(est_05$h0.5, est_05$opt_h)
```

```{r}
# plot estimated VaR on the scatterplot of {Xt, Zt} t=1,...,n  (cutted)
plot(X_cut, Z_cut, ylim=c(min(Z_cut)-0.03,max(Z_cut)+0.02), 
     xlab=expression(X[t]), ylab=expression(Z[t]), main="Monthly Return")
lines(locpoly(est_01$xx,est_01$qq_est,kernel="normal",bandwidth=est_01$opt_h,gridsize=1000), col="blue")
lines(locpoly(est_05$xx,est_05$qq_est,kernel="normal",bandwidth=est_05$opt_h,gridsize=1000), col="red")
lines(locpoly(est_01$xx,est_01$qq_est,kernel="normal",bandwidth=est_01$opt_h,gridsize=1000,degree=2), col="green")
lines(locpoly(est_05$xx,est_05$qq_est,kernel="normal",bandwidth=est_05$opt_h,gridsize=1000,degree=2), col="orange")
legend("topleft",col=c("blue","red"),lty=1, cex=0.8,
       legend=c("Estimated 1% quantile (d=1)","Estimated 5% quantile (d=1)"))
legend("topright",col=c("green","orange"),lty=1, cex=0.8,
       legend=c("Estimated 1% quantile (d=2)","Estimated 5% quantile (d=2)"))
```







### (2) Data without 2020

```{r}
sub_data = mon_data[(mon_data$Date<="2019-12-31"), ]
c(min(sub_data$Date), max(sub_data$Date))
```

```{r}
Z = sub_data$return
n = length(Z)
X = Z[1:(n-1)]
Z = Z[2:n]
Date = sub_data$Date[2:n]
```

```{r}
plot(Date, Z, type="l", ylim=c(min(Z)-0.02,max(Z)+0.02),
     xlab="Month",ylab="return", main="Monthly Return")

# check the distribution of return Zt
hist(Z, breaks=100, freq=FALSE, main="", xlab=expression(Z[t]))
lines(density(Z, adjust=1),col="red",lwd=2) # kernel density estimation
zz = seq(min(Z),max(Z),0.01)
lines(zz, dnorm(zz,mean(Z),sd(Z)), col="blue",lwd=2)

# check the scatterplot of {Xt, Zt} t=1,...,n
plot(X, Z, ylim=c(min(Z)-0.01,max(Z)+0.01), xlab=expression(X[t]), ylab=expression(Z[t]))
```



#### Cut the data

```{r}
cutted = cut_data(X, Z, Date, cutoff=0.05)
X_cut = cutted$X_cut
Z_cut = cutted$Z_cut
Date_cut = cutted$Date_cut
```

```{r}
plot(Date_cut, Z_cut, type="l", ylim=c(min(Z_cut)-0.02,max(Z_cut)+0.02),
     xlab="Month",ylab="return", main="Monthly Return")

# check the distribution of return Zt
hist(Z_cut, breaks=100, freq=FALSE, main="", xlab=expression(Z[t]))
lines(density(Z_cut, adjust=1),col="red",lwd=2) # kernel density estimation
zz_cut = seq(min(Z_cut),max(Z_cut),0.01)
lines(zz_cut, dnorm(zz_cut,mean(Z_cut),sd(Z_cut)), col="blue",lwd=2)

# check the scatterplot of {Xt, Zt} t=1,...,n
plot(X_cut, Z_cut, ylim=c(min(Z_cut)-0.01,max(Z_cut)+0.01), xlab=expression(X[t]), ylab=expression(Z[t]))
```



#### Estimate the conditional quantile

```{r}
# estimate the conditional quantile (cutted)
est_01 = estimate_con_q(X_cut,Z_cut,p=1-0.99, dpill_trim=0.01)
est_05 = estimate_con_q(X_cut,Z_cut,p=1-0.95, dpill_trim=0.01)
c(est_01$h0.5, est_01$opt_h)
c(est_05$h0.5, est_05$opt_h)
```

```{r}
# plot estimated VaR on the scatterplot of {Xt, Zt} t=1,...,n  (cutted)
plot(X_cut, Z_cut, ylim=c(min(Z_cut)-0.03,max(Z_cut)+0.02), 
     xlab=expression(X[t]), ylab=expression(Z[t]), main="Monthly Return without 2020")
lines(locpoly(est_01$xx,est_01$qq_est,kernel="normal",bandwidth=est_01$opt_h,gridsize=1000), col="blue")
lines(locpoly(est_05$xx,est_05$qq_est,kernel="normal",bandwidth=est_05$opt_h,gridsize=1000), col="red")
lines(locpoly(est_01$xx,est_01$qq_est,kernel="normal",bandwidth=est_01$opt_h,gridsize=1000,degree=2), col="green")
lines(locpoly(est_05$xx,est_05$qq_est,kernel="normal",bandwidth=est_05$opt_h,gridsize=1000,degree=2), col="orange")
legend("topleft",col=c("blue","red"),lty=1, cex=0.8,
       legend=c("Estimated 1% quantile (d=1)","Estimated 5% quantile (d=1)"))
legend("topright",col=c("green","orange"),lty=1, cex=0.8,
       legend=c("Estimated 1% quantile (d=2)","Estimated 5% quantile (d=2)"))
```


































